The Weakly Nonlinear Magnetorotational Instability

### 2016-08-16 paper/widegap_mri_paper.tex
fixed typos jeff caught in N20 psi (version multiplied by r^4). rederived coeffificients
added insulating bc description to main text

We solve the system subject to periodic vertical boundary conditions and no-slip, perfectly conducting radial boundary conditions, namely

@@

at $r = r_1, r_2$.

@@

\section{B. Nonlinear Terms}\label{app:nonlinear_terms}

>>>>

We solve the standard MRI system subject to periodic vertical boundary conditions and no-slip, perfectly conducting radial boundary conditions, namely

@@

at $r = r_1, r_2$. To the helical MRI system we apply insulating boundary conditions,

\beq
\partial_r A = k \frac{I_0 (k r)}{I_1 (k r)} A \, \, \mathrm{at} \, \, r = r_1
\eeq

\beq
\partial_r A = - k \frac{K_0 (k r)}{K_1 (k r)} A \, \, \mathrm{at} \, \, r = r_2
\eeq

and $B = 0$ at $r = r_1, r_2$. Here, $I_n$, $K_n$ are the modified Bessel functions of the first and second kind, respectively.

@@

Note that the condition on $B^\dagger$ differs from that on $B$. We take the inner product of the adjoint homogenous solution with Equation \ref{eq:ordere3} to find

\beq
\mathcal{L}\mathbf{V}_3 + \xi \widetilde{\mathcal{H}} \mathbf{V}_3 + \mathcal{D} \partial_T \mathbf{V}_1 + \widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V}_2\nonumber 
+ \xi \mathcal{H}\partial_Z \mathbf{V}_2 + \widetilde{\mathcal{L}}_2 \partial_Z^2 \mathbf{V}_1 - \xi \widetilde{\mathcal{H}} \mathbf{V}_1 + \widetilde{\mathcal{G}} \mathbf{V}_1 + \mathbf{N}_3 = 0.
\eeq

%%%%% NONLINEAR TERMS %%%%%%%%%%%
\section{B. Nonlinear Terms}\label{app:nonlinear_terms}
